%! Author = Atticus Blanco
%! Date = 10/28/2023

% Preamble
\documentclass[11pt]{article}

\title{Introduction to Stained Glass Art for Veterans}
\date{}


% Packages

% Document
\begin{document}

    \maketitle

    \section*{Course Description}
    This 14-week course provides veterans with a creative and therapeutic outlet by introducing them to the art of stained glass. Participants will learn the fundamental techniques of stained glass crafting, from selecting materials to designing and creating their own beautiful stained glass pieces. The course aims to promote relaxation, self-expression, and a sense of accomplishment through art.

    \section*{Learning Objectives}
    By the end of this 14-week course, participants will be able to:
    \begin{itemize}
        \item     Understand the history and significance of stained glass art.
        \item     Safely handle stained glass materials, tools, and equipment.
        \item     Create their own stained glass designs, including patterns and color selection.
        \item     Cut, shape, and assemble stained glass pieces using copper foil or lead came techniques.
        \item     Apply soldering and finishing techniques to complete stained glass projects.
        \item     Gain a sense of satisfaction and pride through the creation of unique stained glass artworks.
    \end{itemize}

    \section*{Course Outline}
    \subsection*{Week 1: Introduction to Stained Glass Art}
    \begin{itemize}
        \item History and significance of stained glass
        \item Safety protocols and equipment overview
        \item Introduction to basic stained glass terminology
\end{itemize}

    \subsection*{Week 2: Design and Pattern Development}
        \begin{itemize}
            \item Creating and transferring patterns
            \item Selecting and sourcing material
            \item Exploring color theory in stained glass design
        \end{itemize}

    \subsection*{Week 3: Cutting and Shaping Glass}
    \begin{itemize}
        \item Glass cutting techniques
        \item Fitting glass pieces together
        \item Practice sessions on basic glass shapes
    \end{itemize}

    \subsection*{Week 4: Copper Foil Technique (Part 1)}
    \begin{itemize}
        Introduction to the copper foil method
        Preparing and cutting glass for copper foil
        Applying copper foil to glass pieces

    \end{itemize}

    \subsection*{Week 5: Copper Foil Technique (Part 2)}
    \begin{itemize}

    \end{itemize}

    \subsection*{Week 6: Lead Came Technique (Part 1)}
    \begin{itemize}

    \end{itemize}

    \subsection*{Week 7: Lead Came Technique (Part 2)}
    \begin{itemize}

    \end{itemize}

    \subsection*{Week 8: Soldering and Finishing (Part 1)}
    \begin{itemize}

    \end{itemize}

    \subsection*{Week 9: Soldering and Finishing (Part 2)}
    \begin{itemize}

    \end{itemize}

    \subsection*{Week 10: Advanced Techniques}
    \begin{itemize}

    \end{itemize}

    \subsection*{Week 11}
    \begin{itemize}

    \end{itemize}

    \subsection*{Week 12}
    \begin{itemize}

    \end{itemize}

    \subsection*{Week 13}
    \begin{itemize}

    \end{itemize}

    \subsection*{Week 14: Final Showcase}
    \begin{itemize}
        \item Preparing and presenting completed stained glass artworks to classmates and invited guests
    \end{itemize}



\end{document}